---
title: "Netflix_Movie_Project"
author: "Syamsi"
date: '2022-05-25'
output: html_document
---

The purpose of this analysis is to practice analyzing and visualizing data, and hopefully communicate some best-practices along the way.

This project will use the following dataset:
Dataset source: https://www.kaggle.com/datasets/victorsoeiro/netflix-tv-shows-and-movies


Bussiness Task:
Which movie had biggest and lowest imdb Score all the time?
Which genre had biggest imdb score for time frame?

```{r packages, include=FALSE}
#load packages
library(tidyverse)
library(plyr)
library(lubridate)
library(tidyr)
library(dplyr)
library(ggplot2)
```

Load csv to R

```
movie_title<-read_csv("titles.csv")
```

Check the data integration, column name, and the size of rows and columns

```
head(movie_title)
colnames(movie_title)
str(movie_title)
dim(movie_title)
```

```{r pressure, echo=FALSE}
drama_score %>% 
  mutate(genres=fct_reorder(genres,desc(imdb_score))) %>%
  ggplot(mapping=aes(x=runtime,y=imdb_score,color=genres))+ 
  geom_point()+
  labs(title="Runtime (minutes) VS imdb score",
       subtitle = "for any movie in 1953-2022")
```